\chapter{FYTGS Requirements}
\label{chap:thesis-preparation}

The requirements are from the \href{https://fytgs.hkust.edu.hk/academics/Academic-Regulations-and-Requirements/Handbook-for-Research-Postgraduate-Studies/guidelines-thesis-preparation}{RPG Handbook}.

\section{Components}

\subsection{Order}

A thesis should contain the following parts in the order shown:

\begin{enumerate}
  \item Title page, containing in this order:
        \begin{enumerate}
          \item Thesis title
          \item Full name of the candidate
          \item Degree for which the thesis is submitted
          \item Name of the University, \emph{i.e.} The Hong Kong University of Science and Technology
          \item Month and year of submission
        \end{enumerate}
  \item Abstract ($\leq$ 300 words.)
  \item Authorization page
  \item Signature page
  \item Acknowledgments
  \item Table of contents
  \item Lists of figures and tables
  \item Thesis body
  \item Bibliography
  \item Appendices and other addenda, if any.
\end{enumerate}

\subsection{Abstract}

Every copy of the thesis must have an English abstract, being a concise summary of the thesis, in 300 words or less.

\subsection{Authorization page}

On this page, students authorize the University to lend or reproduce the thesis.

\begin{enumerate}
  \item The copyright of the thesis as a literary work vests in its author (the student).
  \item The authorization gives HKUST Library a non-exclusive right to make it available for scholarly research.
\end{enumerate}

\subsection{Signature page}

This page provides signatures of the thesis supervisor(s) and Department Head confirming that the thesis is satisfactory.

\subsection{Acknowledgments}

The student is required to declare, in this section, the extent to which assistance has been given by his/her faculty and staff, fellow students, external bodies or others in the collection of materials and data, the design and construction of apparatus, the performance of experiments, the analysis of data, and the preparation of the thesis (including editorial help). In addition, it is appropriate to recognize the supervision and advice given by the thesis supervisor(s) and members of TSC.

\subsection{Bibliography}

The list of sources and references used should be presented in a standard format appropriate to the discipline; formatting should be consistent throughout.

\subsection{Sample pages}
Sample pages of both MPhil and PhD theses are provided here (MPhil / PhD), with specific instructions for formatting page content (centering, spacing, etc.).

\section{Language, Style and Format}

\subsection{Language}

Theses should be written in English.

Students in the School of Humanities and Social Science who are pursuing research work in the areas of Chinese Studies, and who can demonstrate a need to use Chinese to write their theses should seek prior approval from the School via their thesis supervisor and the divisional head.

If approval is granted, students are also required to produce a translation of the title page, authorization page, signature page, table of contents and the abstract in English.

\subsection{Pagination}

\begin{enumerate}
  \item All pages, starting with the Title page should be numbered.
  \item All page numbers should be centered, at the bottom of each page.
  \item Page numbers of materials preceding the body of the text should be in small Roman numerals.
  \item Page numbers of the text, beginning with the first page of the first chapter and continuing through the bibliography, including any pages with tables, maps, figures, photographs, etc., and any subsequent appendices, should be in Arabic numerals.
  \item Start a new page after each chapter or section but not after a sub-section.
\end{enumerate}

\emph{Note: That means the Title page will be page i; the first page of the first chapter will be page 1.}

\subsection{Format}

\begin{enumerate}
  \item A conventional font, size 12-point, 10 to 12 characters per inch must be used.
  \item One-and-a-half line spacing should be used throughout the thesis, except for abstracts, indented quotations or footnotes where single line spacing may be used.
  \item All margins—top, bottom, sides—should be consistently 25mm (or no more than 30mm) in width. The same margin should be used throughout a thesis. Exceptionally, margins of a different size may be used when the nature of the thesis requires it.
\end{enumerate}

\subsection{Footnotes}

\begin{enumerate}
  \item Footnotes may be placed at the bottom of the page, at the end of each chapter or after the end of the thesis body.
  \item Like references, footnotes should be presented in a standard format appropriate to the discipline.
  \item Both the position and format of footnotes should be consistent throughout the thesis.
\end{enumerate}

\subsection{Appendices}

The format of each appended item should be consistent with the nature of that item, whether text, diagram, figure, etc., and should follow the guidelines for that item as listed here.

\subsection{Figures, Tables and Illustrations}

Figures, tables, graphs, etc., should be placed as close as possible to the text they illustrate. Charts, graphs, maps, and tables that are larger than a standard page should be provided as appendices.

\subsection{Photographs/Images}

\begin{enumerate}
  \item High contrast photos should be used because they reproduce well. Photographs with a glossy finish and those with dark backgrounds should be avoided.
  \item Images should be dense enough to provide 300 ppi for printing and 72 dpi for viewing.
\end{enumerate}

\subsection{Additional Materials}

Raw files, datasets, media files, and high resolution photographs/images of any format can be included.

\emph{Note: Students should get approval from their department head before deviating from any of the above requirements concerning paper size, font, margins, etc. }
